Rotations and Insecticide Resistance initial plots

### 2017-10-05 inst/documents/rotations_notes.Rmd
active and refuge plotted on same sub-plot
build doc
allow starting frequencies to be set

>>>>

I now have run_rot() working for flexible numbers of insecticides (1-5).

Done : Next, get active and refuge onto the same plots.

# TODO
~ test setting inputs correctly (move away from hardcoded test functions)
~ find what went wrong when I set fitnesses
~ get Ian to pull changes

# state of play
~ rotations1.Rmd : example plots
